---
title: "X24067_Pan_Heart Age"
author: "Yue Pan"
date: "`r Sys.Date()`"
format:
  html:
    self-contained: true
    toc: true
    toc-title: "Outline"
    toc-depth: 3
    toc-location: body
    number-sections: true
    code-fold: true
    code-summary: "Show code"
    code-tools: true
    code-copy: true
    page-layout: full
    smooth-scroll: true
knitr:
  opts_chunk:
    collapse: true
    echo: true
    message: true
    warning: true
    error: true
    comment: ""
    R.options:
      digits: 3
editor: visual
bibliography: [references.bib, packages.bib]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# ---- Packages ----
library(here)
library(conflicted)
library(readr)
library(dplyr)
library(stringr)
library(forcats)
library(ggplot2)
library(scales)
library(purrr)      # Required for map/map_dfr functions
library(patchwork)

# ---- Reporting Packages ----
library(gtsummary)
library(sumExtras)
library(gt)
library(labelled)
library(haven)      # Read SAS data

# ---- Modeling Packages ----
library(broom)       # For tidying model outputs
library(emmeans)     # For marginal means & interactions
library(mice)        # For multiple imputation

# Apply JAMA-style theme
sumExtras::use_jama_theme()

# Conflict preferences
conflict_prefer("filter", "dplyr", quiet = TRUE)
conflict_prefer("select", "dplyr", quiet = TRUE)
conflict_prefer("recode", "dplyr", quiet = TRUE)
conflict_prefer("lag", "dplyr", quiet = TRUE)
conflict_prefer("var_label", "labelled", quiet = TRUE)

options(dplyr.summarise.inform = FALSE)
options(scipen = 999)
```

# Introduction

This is for X24067_Pan_Heart Age. This analysis compares Heart Age outcomes between People Living Without HIV (PLWoH) and People Living With HIV (PLWH) (combining Seroprevalent and Seroconverter groups).

Output order matches `X24067_Tables and Figures.docx`:
Table 1 → Table 2 (merged S4+S5) → Table 3 (merged reg, Fig 1A+B) → Suppl Tables S1–S3 → Suppl S4 (MICE, was S6) → Suppl S5 (interaction, was S7) → Table 4 → Suppl S6 (sex-strat, was S8) → Suppl Fig S1 → Suppl Fig S2 → Suppl Figs S3–S5.

## 0. Load and Clean Data

```{r labels, include=TRUE}
# ---- 1. SETUP PATHS (cross-platform) ----
# Candidate locations for prevent_risk.sas7bdat, checked in order:
#   1. Windows Box path (original)
#   2. Mac: place the file in X24067_HA PREVENT/data/prevent_risk.sas7bdat
#      relative to the project root (ECG paper/)
candidate_paths <- c(
  # Windows
  "C:/Users/panyue/Box/Yue Pan from old laptop 2015/DR FEASTER/Other Professors/111 CCS/X24067_Pan_Heart Age/SAS Output/prevent_risk.sas7bdat",
  # Mac — relative to this script (analysis/ folder)
  file.path(dirname(normalizePath(if (nzchar(knitr::current_input()))
                                    knitr::current_input() else ".")),
            "..", "data", "prevent_risk.sas7bdat"),
  # Mac fallback — relative to working directory
  file.path("..", "data", "prevent_risk.sas7bdat"),
  file.path("data", "prevent_risk.sas7bdat")
)

input_path <- Filter(file.exists, candidate_paths)[1]

if (is.null(input_path) || is.na(input_path)) {
  stop(paste0(
    "prevent_risk.sas7bdat not found. On Mac, copy it to:\n",
    "  X24067_HA PREVENT/data/prevent_risk.sas7bdat\n",
    "Paths tried:\n",
    paste(" -", candidate_paths, collapse = "\n")
  ))
}

message("Reading data from: ", input_path)
prevent_risk <- read_sas(input_path)

# Output figures folder: save next to this script in ../figures/
figures_dir <- file.path(dirname(normalizePath(if (nzchar(knitr::current_input()))
                                                 knitr::current_input() else ".")),
                          "..", "figures")
if (!dir.exists(figures_dir)) dir.create(figures_dir, recursive = TRUE)

# Legacy project_dir for any remaining references
project_dir <- dirname(input_path)

# ---- 2. FILTER & CLEAN ----
analysis_clean <- prevent_risk %>%
  # Filter to one row per CCSID (Baseline/First Visit logic)
  arrange(CCSID, VISIT) %>%
  group_by(CCSID) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(
    # --- HIV STATUS (PLWoH vs PLWH) ---
    hiv_status = case_when(
      STATUS == 1 ~ "PLWoH",
      STATUS %in% c(2, 4, 5) ~ "PLWH",
      TRUE ~ NA_character_
    ),
    hiv_status = factor(hiv_status, levels = c("PLWoH", "PLWH")),

    # --- RACE/ETHNICITY (4 Groups) ---
    race_eth_4cat = case_when(
      HISP == 1 ~ "Hispanic",
      HISP == 0 & RACE == 5 ~ "Non-Hispanic White",
      HISP == 0 & RACE == 4 ~ "Non-Hispanic Black",
      TRUE ~ "Other"
    ),
    race_eth_4cat = factor(race_eth_4cat,
                           levels = c("Non-Hispanic White",
                                      "Non-Hispanic Black",
                                      "Hispanic",
                                      "Other")),

    # --- REGION ---
    REGION_factor = factor(REGION,
                           levels = c(0, 1, 2, 3, 4),
                           labels = c("West (CA)",
                                      "Northeast (NY)",
                                      "Mid-Atlantic (DC, MD)",
                                      "South (AL, FL, GA, MS, NC)",
                                      "Midwest (IL, OH, PA)")),

    SEX = factor(SEX, levels = c("Female", "Male")),

    # --- CLINICAL BINARIES (0=No, 1=Yes) ---
    HYPERTENSIONMED = factor(ifelse(HYPERTENSIONMED == 1, "Yes", "No"), levels = c("No", "Yes")),
    STATINMED = factor(ifelse(STATINMED == 1, "Yes", "No"), levels = c("No", "Yes")),

    # Smoking (0/10=No, 1/11=Yes)
    CURSMOKE_BIN = factor(ifelse(CURSMOKE %in% c(1, 11), "Yes", "No"), levels = c("No", "Yes")),

    # Diabetes
    DIAB_BIN = factor(ifelse(DIAB_BIN == 1, "Yes", "No"), levels = c("No", "Yes")),

    # --- CATEGORIES ---
    age_group = case_when(
      AGEATVIS >= 30 & AGEATVIS < 40 ~ "30-39",
      AGEATVIS >= 40 & AGEATVIS < 50 ~ "40-49",
      AGEATVIS >= 50 & AGEATVIS < 60 ~ "50-59",
      AGEATVIS >= 60 & AGEATVIS < 70 ~ "60-69",
      AGEATVIS >= 70 ~ "70+",
      TRUE ~ NA_character_
    ),

    bmi_cat = case_when(
      BMI < 18.5 ~ "Underweight",
      BMI >= 18.5 & BMI < 25 ~ "Normal",
      BMI >= 25 & BMI < 30 ~ "Overweight",
      BMI >= 30 ~ "Obese",
      TRUE ~ NA_character_
    ) %>% factor(levels = c("Underweight", "Normal", "Overweight", "Obese")),

    sbp_cat = case_when(
      SYSTOLIC < 120 ~ "Normal (<120)",
      SYSTOLIC >= 120 & SYSTOLIC < 130 ~ "Elevated (120-129)",
      SYSTOLIC >= 130 & SYSTOLIC < 140 ~ "Stage 1 HTN (130-139)",
      SYSTOLIC >= 140 ~ "Stage 2 HTN (>=140)",
      TRUE ~ NA_character_
    ),

    chol_cat = case_when(
      CHOL < 200 ~ "Desirable (<200)",
      CHOL >= 200 & CHOL < 240 ~ "Borderline (200-239)",
      CHOL >= 240 ~ "High (>=240)",
      TRUE ~ NA_character_
    ),

    egfr_cat = case_when(
      EGFR_CKDEPI < 60 ~ "Low (<60)",
      EGFR_CKDEPI >= 60 & EGFR_CKDEPI <= 90 ~ "Moderate (60-90)",
      EGFR_CKDEPI > 90 ~ "High (>90)",
      TRUE ~ NA_character_
    ),

    # --- OUTCOME FLAGS ---
    had5  = factor(ifelse(heart_age_deviation >= 5, "Yes", "No"), levels = c("No", "Yes")),
    had10 = factor(ifelse(heart_age_deviation >= 10, "Yes", "No"), levels = c("No", "Yes")),
    ha_gt_age = factor(ifelse(heart_age > AGEATVIS, "Yes", "No"), levels = c("No", "Yes")),

    # --- HIV SPECIFIC ---
    cd4_cat = case_when(
      CD4N < 200 ~ "<200 cells/mm3",
      CD4N >= 200 & CD4N < 500 ~ "200-499 cells/mm3",
      CD4N >= 500 ~ ">=500 cells/mm3",
      TRUE ~ NA_character_
    ) %>% factor(levels = c("<200 cells/mm3", "200-499 cells/mm3", ">=500 cells/mm3"))

  ) %>%
  filter(!is.na(hiv_status), !is.na(BMI), !is.na(CHOL), !is.na(SYSTOLIC))

# --- SET VARIABLE LABELS ---
var_label(analysis_clean) <- list(
  AGEATVIS = "Age (years)",
  age_group = "Age Group",
  SEX = "Biological Sex",
  race_eth_4cat = "Race/Ethnicity",
  REGION_factor = "Region",
  BMI = "Body Mass Index (kg/m^2)",
  bmi_cat = "BMI Category",
  SYSTOLIC = "Systolic BP (mmHg)",
  sbp_cat = "SBP Category",
  CHOL = "Total Cholesterol (mg/dL)",
  chol_cat = "Cholesterol Category",
  HDLCT = "HDL Cholesterol (mg/dL)",
  EGFR_CKDEPI = "eGFR (CKD-EPI)",
  egfr_cat = "eGFR Category",
  CURSMOKE_BIN = "Current Smoker",
  DIAB_BIN = "Diabetes",
  HYPERTENSIONMED = "Anti-hypertensive Meds",
  STATINMED = "Statin Use",
  prevent_risk = "PREVENT 10-Year Risk",
  heart_age = "Heart Age (years)",
  heart_age_deviation = "Heart Age Deviation (HAD)",
  had5 = "HAD ≥ 5 Years",
  had10 = "HAD ≥ 10 Years",
  ha_gt_age = "Heart Age > Chronological Age",
  CD4N = "CD4 Count (cells/mm3)",
  cd4_cat = "CD4 Count Category"
)

# ---- 3. CALCULATE TOTAL N FOR HEADERS ----
n_plwoh <- sum(analysis_clean$hiv_status == "PLWoH", na.rm = TRUE)
n_plwh  <- sum(analysis_clean$hiv_status == "PLWH", na.rm = TRUE)
```

------------------------------------------------------------------------

## Table 1: Descriptive Characteristics

```{r table1, include=TRUE}
table1 <- analysis_clean %>%
  select(hiv_status, AGEATVIS, age_group, SEX, race_eth_4cat, REGION_factor,
         BMI, bmi_cat, SYSTOLIC, sbp_cat, CHOL, chol_cat, HDLCT,
         EGFR_CKDEPI, egfr_cat, CURSMOKE_BIN, DIAB_BIN,
         HYPERTENSIONMED, STATINMED, prevent_risk,
         heart_age, heart_age_deviation, had5, had10,
         CD4N, cd4_cat) %>%
  tbl_summary(
    by = hiv_status,
    missing = "no",
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = list(all_continuous() ~ 1, all_categorical() ~ c(0, 1))
  ) %>%
  add_p() %>%
  add_overall() %>%
  bold_p() %>%
  modify_caption("**Table 1. Descriptive characteristics of 2,729 participants by HIV serostatus in the MWCCS, 2020-2024.**") %>%
  bold_labels()

table1
```

------------------------------------------------------------------------

<!-- Table 2 output appears here in document flow but is generated after strat_functions are defined.
     See the table2_prevalence_merged chunk below (placed after strat_functions). -->

------------------------------------------------------------------------

## Table 3 and Figure 1: Multivariable Regression (Merged Panels A + B)

```{r modeling_setup}
# ==============================================================================
#  DATA SETUP & RECODING FOR MODELING
# ==============================================================================

theme_gtsummary_journal(journal = "jama")

modeling_data <- analysis_clean %>%
  mutate(
    # 1. RESCALE AGE: Convert years to "Decades" so OR is meaningful
    age_decade = AGEATVIS / 10,

    # 2. HIV STATUS: Set reference to 'PLWoH'
    hiv_status = fct_relevel(hiv_status, "PLWoH"),

    # 3. SEX: Set reference to Male
    SEX = fct_relevel(SEX, "Male"),

    # 4. RACE: Set reference to White
    race_eth_4cat = fct_relevel(race_eth_4cat, "Non-Hispanic White"),

    # 5. OUTCOMES: Ensure "No" is reference
    had5 = fct_relevel(had5, "No"),

    # 6. HIV SPECIFIC VARS (for Table 4)
    viral_suppression = case_when(
      UD_VL == 1 ~ "Undetectable",
      UD_VL %in% c(2, 3) ~ "Detectable",
      TRUE ~ NA_character_
    ),
    viral_suppression = factor(viral_suppression, levels = c("Undetectable", "Detectable")),

    # CD4 Count (scaled per 100 cells for readability)
    cd4_100 = CD4N / 100
  )
```

### Table 3 (merged) and Figure 1 (combined panels A + B)

```{r table3_merged_and_fig1}
# ---- Models (unchanged) ----
lm_aim1 <- lm(
  heart_age_deviation ~ hiv_status + age_decade + SEX + race_eth_4cat + REGION_factor,
  data = modeling_data
)

glm_aim1 <- glm(
  had5 ~ hiv_status + age_decade + SEX + race_eth_4cat + REGION_factor,
  data = modeling_data,
  family = binomial
)

# ---- Individual gtsummary tables (with global p, used as source for merge) ----
tbl_aim1_linear <- tbl_regression(
  lm_aim1,
  estimate_fun = ~ style_sigfig(.x, digits = 2),
  label = list(
    hiv_status ~ "HIV Serostatus",
    age_decade ~ "Age (per 10 years)",
    SEX ~ "Sex",
    race_eth_4cat ~ "Race/Ethnicity",
    REGION_factor ~ "Region"
  )
) %>%
  bold_p()
# Note: add_global_p() removed — it moves p-values from level rows to variable
# label rows, which breaks add_significance_stars on level rows (NHB, Female, etc.)

tbl_aim1_logistic <- tbl_regression(
  glm_aim1,
  exponentiate = TRUE,
  label = list(
    hiv_status ~ "HIV Serostatus",
    age_decade ~ "Age (per 10 years)",
    SEX ~ "Sex",
    race_eth_4cat ~ "Race/Ethnicity",
    REGION_factor ~ "Region"
  )
) %>%
  bold_p()

# ---- Replace p-value columns with significance stars ----
tbl_linear_stars <- tbl_aim1_linear %>%
  add_significance_stars(
    hide_p   = TRUE,
    hide_ci  = FALSE,
    hide_se  = TRUE
  ) %>%
  # Merge stars-augmented estimate with formatted CI string; pattern must include {stars}
  modify_column_merge(
    pattern = "{estimate} ({ci}){stars}",
    rows    = !is.na(ci)
  ) %>%
  modify_column_hide(columns = any_of(c("conf.low", "conf.high", "std.error", "ci"))) %>%
  modify_header(estimate ~ "**β (95% CI)**")

tbl_logistic_stars <- tbl_aim1_logistic %>%
  add_significance_stars(
    hide_p   = TRUE,
    hide_ci  = FALSE,
    hide_se  = TRUE
  ) %>%
  modify_column_merge(
    pattern = "{estimate} ({ci}){stars}",
    rows    = !is.na(ci)
  ) %>%
  modify_column_hide(columns = any_of(c("conf.low", "conf.high", "std.error", "ci"))) %>%
  modify_header(estimate ~ "**OR (95% CI)**")

# ---- Merge side-by-side as Table 3 ----
tbl_T3 <- tbl_merge(
  tbls = list(tbl_linear_stars, tbl_logistic_stars),
  tab_spanner = c(
    "**Panel A: Linear regression (continuous HAD)**",
    "**Panel B: Logistic regression (HAD ≥5 years)**"
  )
) %>%
  modify_caption(
    "**Table 3. Multivariable regression predicting heart age deviation. Panel A: linear regression (continuous HAD, years). Panel B: logistic regression (elevated HAD ≥5 years).**"
  ) %>%
  modify_footnote(
    update = everything() ~
      "Reference categories: HIV-negative, male, Non-Hispanic White, West US region. Age modeled per 10-year increment. OR = Odds Ratio. *p<0.05; **p<0.01; ***p<0.001."
  )

tbl_T3

# ---- Figure 1A: Logistic forest plot (Panel A) ----
plot_data_aim1 <- broom::tidy(glm_aim1, conf.int = TRUE, exponentiate = TRUE) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term_label = case_when(
      term == "age_decade" ~ "Age (per 10 years)",
      term == "hiv_statusPLWH" ~ "HIV-positive (vs HIV-negative)",
      term == "SEXFemale" ~ "Female (vs male)",
      term == "race_eth_4catNon-Hispanic Black" ~ "Non-Hispanic Black (vs Non-Hispanic White)",
      term == "race_eth_4catHispanic" ~ "Hispanic (vs Non-Hispanic White)",
      term == "race_eth_4catOther" ~ "Other race/ethnicity (vs Non-Hispanic White)",
      term == "REGION_factorNortheast (NY)" ~ "Northeast (vs West)",
      term == "REGION_factorMid-Atlantic (DC, MD)" ~ "Mid-Atlantic (vs West)",
      term == "REGION_factorSouth (AL, FL, GA, MS, NC)" ~ "South (vs West)",
      term == "REGION_factorMidwest (IL, OH, PA)" ~ "Midwest (vs West)",
      TRUE ~ term
    ),
    term_label = fct_reorder(term_label, estimate)
  )

fig1a_obj <- ggplot(plot_data_aim1, aes(y = term_label, x = estimate, xmin = conf.low, xmax = conf.high)) +
  geom_point(color = "#0072B2", size = 3) +
  geom_errorbar(width = 0.2, color = "#0072B2") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "gray50") +
  labs(
    title = "A. Predictors of elevated HAD (≥5 years)",
    subtitle = "Logistic regression; ref: HIV-negative, male, Non-Hispanic White, West",
    x = "Odds ratio (95% CI)",
    y = NULL
  ) +
  theme_minimal() +
  theme(plot.title = element_text(face = "bold"))

fig1a_obj

# RETIRED standalone save (kept for reference):
# ggsave(filename = file.path(figures_dir, "Fig1_HAD5_LogisticForestPlot.png"),
#        width = 8, height = 6, dpi = 300, bg = "white")
# Combined Fig 1 is saved after Panel B is built (see table4_and_fig1b chunk).
```

------------------------------------------------------------------------

## Supplemental Tables S1–S3: Stratified Outcomes by Subgroup (S4/S5 promoted to main Table 2)

```{r strat_setup}
# Define the subgroups for stratification
row_vars <- c("age_group", "SEX", "race_eth_4cat", "REGION_factor", "bmi_cat",
              "sbp_cat", "chol_cat", "egfr_cat", "CURSMOKE_BIN", "DIAB_BIN",
              "HYPERTENSIONMED", "STATINMED")

var_labels_map <- c(
  "age_group" = "Age Group",
  "SEX" = "Sex",
  "race_eth_4cat" = "Race/Ethnicity",
  "REGION_factor" = "Region",
  "bmi_cat" = "BMI Category",
  "sbp_cat" = "SBP Category",
  "chol_cat" = "Cholesterol Category",
  "egfr_cat" = "eGFR Category",
  "CURSMOKE_BIN" = "Current Smoker",
  "DIAB_BIN" = "Diabetes",
  "HYPERTENSIONMED" = "BP Meds",
  "STATINMED" = "Statin Use"
)
```

```{r strat_functions}
# Function to create tables for continuous outcomes (Mean/SD)
create_strat_continuous <- function(data, outcome_var, caption) {

  var_labels_map <- c(
    "age_group" = "Age Group",
    "SEX" = "Sex",
    "race_eth_4cat" = "Race/Ethnicity",
    "REGION_factor" = "Region",
    "bmi_cat" = "BMI Category",
    "sbp_cat" = "SBP Category",
    "chol_cat" = "Cholesterol Category",
    "egfr_cat" = "eGFR Category",
    "CURSMOKE_BIN" = "Current Smoker",
    "DIAB_BIN" = "Diabetes",
    "HYPERTENSIONMED" = "BP Meds",
    "STATINMED" = "Statin Use"
  )

  tbl_list <- list()

  for (var in row_vars) {
    if(is.factor(data[[var]])) lvls <- levels(data[[var]]) else lvls <- sort(unique(na.omit(data[[var]])))

    rows_list <- lapply(lvls, function(lvl) {
      subset_data <- data %>% filter(.data[[var]] == lvl)
      if(nrow(subset_data) == 0) return(NULL)

      subset_data %>%
        select(hiv_status, all_of(outcome_var)) %>%
        tbl_summary(
          by = hiv_status,
          statistic = all_continuous() ~ "{mean} ({sd})",
          digits = all_continuous() ~ 2,
          label = list(all_of(outcome_var) ~ lvl),
          missing = "no"
        ) %>%
        add_p(test = all_continuous() ~ "t.test") %>%
        bold_p() %>%
        modify_header(label = "**Characteristic**")
    })

    rows_list <- rows_list[!sapply(rows_list, is.null)]
    tbl_list[[var]] <- tbl_stack(rows_list)
  }

  header_plwoh <- paste0("**PLWoH**\nN = ", format(n_plwoh, big.mark = ","))
  header_plwh  <- paste0("**PLWH**\nN = ", format(n_plwh, big.mark = ","))

  tbl_stack(tbl_list, group_header = var_labels_map[row_vars]) %>%
    modify_caption(caption) %>%
    bold_labels() %>%
    modify_header(stat_1 = header_plwoh, stat_2 = header_plwh)
}

# Function to create tables for binary outcomes (Prevalence n/N %)
create_strat_prevalence <- function(data, outcome_var, caption) {

  tbl_list <- list()

  for (var in row_vars) {
    if(is.factor(data[[var]])) lvls <- levels(data[[var]]) else lvls <- sort(unique(na.omit(data[[var]])))

    rows_list <- lapply(lvls, function(lvl) {
      subset_data <- data %>% filter(.data[[var]] == lvl)
      if(nrow(subset_data) == 0) return(NULL)

      subset_data %>%
        select(hiv_status, all_of(outcome_var)) %>%
        tbl_summary(
          by = hiv_status,
          statistic = all_categorical() ~ "{n}/{N} ({p}%)",
          digits = all_categorical() ~ 1,
          label = list(all_of(outcome_var) ~ lvl),
          missing = "no",
          value = list(all_of(outcome_var) ~ "Yes")
        ) %>%
        add_p() %>%
        bold_p() %>%
        modify_header(label = "**Characteristic**")
    })

    rows_list <- rows_list[!sapply(rows_list, is.null)]
    tbl_list[[var]] <- tbl_stack(rows_list)
  }

  header_plwoh <- paste0("**PLWoH**\nN = ", format(n_plwoh, big.mark = ","))
  header_plwh  <- paste0("**PLWH**\nN = ", format(n_plwh, big.mark = ","))

  tbl_stack(tbl_list, group_header = var_labels_map[row_vars]) %>%
    modify_caption(caption) %>%
    bold_labels() %>%
    modify_header(stat_1 = header_plwoh, stat_2 = header_plwh)
}
```

#### Table 2: Prevalence Tables (Combined S4+S5, Promoted from Supplement)

```{r table2_prevalence_merged}
# Build Table 2 manually using gt::gt() with a computed tibble.
# This avoids the gtsummary tbl_merge / tbl_stack row-alignment quirks
# (extra label rows, wrong subgroup-level N counts).
# Depends on row_vars, var_labels_map, n_plwoh, n_plwh from strat_setup.

library(gt)
library(tidyr)

# Helper: compute one prevalence cell + chi-square significance star
prev_cell <- function(subset_data, outcome_var) {
  d <- subset_data %>% filter(!is.na(.data[[outcome_var]]), !is.na(hiv_status))
  if (nrow(d) == 0) {
    return(list(plwoh_str = "—", plwh_str = "—", p = NA_real_, stars = ""))
  }
  d_plwoh <- d %>% filter(hiv_status == "PLWoH")
  d_plwh  <- d %>% filter(hiv_status == "PLWH")
  n_plwoh_yes <- sum(d_plwoh[[outcome_var]] == "Yes", na.rm = TRUE)
  N_plwoh     <- nrow(d_plwoh)
  n_plwh_yes  <- sum(d_plwh[[outcome_var]]  == "Yes", na.rm = TRUE)
  N_plwh      <- nrow(d_plwh)

  pct_plwoh <- if (N_plwoh > 0) 100 * n_plwoh_yes / N_plwoh else NA_real_
  pct_plwh  <- if (N_plwh  > 0) 100 * n_plwh_yes  / N_plwh  else NA_real_

  # Chi-square test (suppress warnings for small expected counts)
  p <- tryCatch({
    suppressWarnings(chisq.test(table(d$hiv_status, d[[outcome_var]]))$p.value)
  }, error = function(e) NA_real_)

  stars <- dplyr::case_when(
    is.na(p)    ~ "",
    p < 0.001   ~ "***",
    p < 0.01    ~ "**",
    p < 0.05    ~ "*",
    TRUE        ~ ""
  )

  list(
    plwoh_str = sprintf("%d/%d (%.1f%%)", n_plwoh_yes, N_plwoh, pct_plwoh),
    plwh_str  = sprintf("%d/%d (%.1f%%)%s", n_plwh_yes,  N_plwh,  pct_plwh, stars),
    p         = p,
    stars     = stars
  )
}

# Build the long-form data with one row per (var, lvl)
t2_rows <- purrr::map_dfr(row_vars, function(var) {
  lvls <- if (is.factor(analysis_clean[[var]])) {
    levels(analysis_clean[[var]])
  } else {
    sort(unique(na.omit(analysis_clean[[var]])))
  }

  purrr::map_dfr(lvls, function(lvl) {
    subset_data <- analysis_clean %>% filter(.data[[var]] == lvl)
    if (nrow(subset_data) == 0) return(NULL)

    r_had5  <- prev_cell(subset_data, "had5")
    r_hagt  <- prev_cell(subset_data, "ha_gt_age")

    tibble::tibble(
      var_group    = unname(var_labels_map[var]),
      Characteristic = as.character(lvl),
      plwoh_had5   = r_had5$plwoh_str,
      plwh_had5    = r_had5$plwh_str,
      plwoh_hagt   = r_hagt$plwoh_str,
      plwh_hagt    = r_hagt$plwh_str
    )
  })
})

# Build the gt table with grouped rows and tab_spanner for outcomes
header_plwoh_md <- paste0("PLWoH<br>N = ", format(n_plwoh, big.mark = ","))
header_plwh_md  <- paste0("PLWH<br>N = ",  format(n_plwh,  big.mark = ","))

tbl_T2 <- t2_rows %>%
  gt(groupname_col = "var_group", rowname_col = "Characteristic") %>%
  tab_header(
    title = md("**Table 2. Prevalence of elevated heart age deviation (HAD ≥5 years) and heart age exceeding chronological age, by HIV serostatus and clinical subgroups.**")
  ) %>%
  cols_label(
    plwoh_had5 = md(header_plwoh_md),
    plwh_had5  = md(header_plwh_md),
    plwoh_hagt = md(header_plwoh_md),
    plwh_hagt  = md(header_plwh_md)
  ) %>%
  tab_spanner(label = md("**HAD ≥5 years**"),                       columns = c(plwoh_had5, plwh_had5)) %>%
  tab_spanner(label = md("**Heart age > chronological age**"),      columns = c(plwoh_hagt, plwh_hagt)) %>%
  tab_stubhead(label = md("**Characteristic**")) %>%
  tab_options(
    row_group.font.weight = "bold",
    table.font.size       = px(13)
  ) %>%
  tab_footnote(
    footnote = md("Values are n/N (%). p-values from chi-square test comparing PLWoH vs PLWH within each subgroup. *p<0.05; **p<0.01; ***p<0.001. PLWoH = people without HIV; PLWH = people with HIV.")
  )

tbl_T2
```

#### Supplemental Table S1: PREVENT 10-Year Risk

```{r suppl_s1}
create_strat_continuous(
  analysis_clean,
  "prevent_risk",
  "**Supplemental Table S1. PREVENT 10-year cardiovascular risk (mean [SD]) by HIV serostatus and clinical subgroups.**"
)
```

#### Supplemental Table S2: Heart Age Deviation

```{r suppl_s2}
create_strat_continuous(
  analysis_clean,
  "heart_age_deviation",
  "**Supplemental Table S2. Heart age deviation (years; mean [SD]) by HIV serostatus and clinical subgroups.**"
)
```

#### Supplemental Table S3: Heart Age (Years)

```{r suppl_s3}
create_strat_continuous(
  analysis_clean,
  "heart_age",
  "**Supplemental Table S3. Heart age (years; mean [SD]) by HIV serostatus and clinical subgroups.**"
)
```

#### Supplemental Tables S4 and S5: RETIRED — promoted to main Table 2

```{r suppl_s4_retired, eval=FALSE}
# RETIRED: S4 (HAD >=5 prevalence) and S5 (HA > chron age prevalence) are now combined
# and promoted to main Table 2 (see table2_prevalence_merged chunk above).
# Kept here as comments for traceability; eval=FALSE prevents execution.

# create_strat_prevalence(analysis_clean, "had5",
#   "**Supplemental Table S4. Prevalence of heart age deviation >=5 years...**")
# create_strat_prevalence(analysis_clean, "ha_gt_age",
#   "**Supplemental Table S5. Prevalence of heart age > chronological age...**")
```

#### Supplemental Table S6: Sex-Stratified Descriptive Characteristics by HIV Serostatus (was S8)

```{r suppl_s6_sex_hiv}
fmt_mean_sd <- function(x, digits = 1) {
  sprintf(
    paste0("%.", digits, "f (%.", digits, "f)"),
    mean(x, na.rm = TRUE),
    stats::sd(x, na.rm = TRUE)
  )
}

fmt_n_pct <- function(x, digits = 1) {
  n <- length(x)
  yes <- sum(x, na.rm = TRUE)
  sprintf(paste0("%d (%.", digits, "f)"), yes, 100 * yes / n)
}

analysis_output_dir <- dirname(normalizePath(
  if (nzchar(knitr::current_input())) knitr::current_input() else ".",
  mustWork = FALSE
))

sex_hiv_supp_table <- analysis_clean %>%
  filter(!is.na(SEX), !is.na(hiv_status)) %>%
  group_by(SEX, hiv_status) %>%
  summarise(
    N = n(),
    `Age, mean (SD)` = fmt_mean_sd(AGEATVIS),
    `Non-Hispanic Black, n (%)` = fmt_n_pct(race_eth_4cat == "Non-Hispanic Black"),
    `Southern region, n (%)` = fmt_n_pct(REGION_factor == "South (AL, FL, GA, MS, NC)"),
    `Current smoking, n (%)` = fmt_n_pct(CURSMOKE_BIN == "Yes"),
    `BMI, mean (SD)` = fmt_mean_sd(BMI),
    `Obesity, n (%)` = fmt_n_pct(bmi_cat == "Obese"),
    `Diabetes, n (%)` = fmt_n_pct(DIAB_BIN == "Yes"),
    `Systolic BP, mean (SD)` = fmt_mean_sd(SYSTOLIC),
    `Stage 2 hypertension, n (%)` = fmt_n_pct(sbp_cat == "Stage 2 HTN (>=140)"),
    `Heart age deviation, mean (SD)` = fmt_mean_sd(heart_age_deviation),
    `HAD >=5 years, n (%)` = fmt_n_pct(had5 == "Yes"),
    .groups = "drop"
  ) %>%
  rename(
    Sex = SEX,
    `HIV status` = hiv_status
  ) %>%
  arrange(Sex, `HIV status`)

write_csv(
  sex_hiv_supp_table,
  file.path(analysis_output_dir, "x24067_supplementary_sex_hiv_table.csv")
)

write_lines(
  c(
    "# Supplemental Table S6 (was S8)",
    "",
    "Sex-stratified descriptive characteristics and heart age deviation by HIV serostatus.",
    "",
    knitr::kable(sex_hiv_supp_table, format = "markdown")
  ),
  file.path(analysis_output_dir, "x24067_supplementary_sex_hiv_table.md")
)

sex_hiv_supp_table
```

------------------------------------------------------------------------

## Table 4 and Figure 1B: HIV Severity Model (PLWH Only)

```{r table4_and_fig1b}
# Filter to PLWH with complete viral load and CD4 data
plwh_data <- modeling_data %>%
  filter(hiv_status == "PLWH") %>%
  filter(!is.na(UD_VL), !is.na(CD4N))

lm_hiv_severity <- lm(
  heart_age_deviation ~ viral_suppression + cd4_100 + age_decade + SEX + race_eth_4cat,
  data = plwh_data
)

tbl_hiv_severity <- tbl_regression(
  lm_hiv_severity,
  estimate_fun = ~ style_sigfig(.x, digits = 2),
  label = list(
    viral_suppression ~ "Viral Suppression (Ref: Undetectable)",
    cd4_100 ~ "CD4 Count (per 100 cells)",
    age_decade ~ "Age (per 10 years)",
    SEX ~ "Sex",
    race_eth_4cat ~ "Race/Ethnicity"
  )
) %>%
  bold_p() %>%
  modify_caption("**Table 4. HIV severity model (people with HIV only): viral load and CD4 count predicting heart age deviation.**")

tbl_hiv_severity

# ---- Figure 1B: HIV severity forest plot (Panel B of combined Fig 1) ----
plot_hiv <- broom::tidy(lm_hiv_severity, conf.int = TRUE) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term_label = case_when(
      term == "viral_suppressionDetectable" ~ "Detectable viral load (vs undetectable)",
      term == "cd4_100" ~ "CD4 count (per 100 cells/mm³)",
      term == "age_decade" ~ "Age (per 10 years)",
      term == "SEXFemale" ~ "Female (vs male)",
      term == "race_eth_4catNon-Hispanic Black" ~ "Non-Hispanic Black (vs Non-Hispanic White)",
      term == "race_eth_4catHispanic" ~ "Hispanic (vs Non-Hispanic White)",
      term == "race_eth_4catOther" ~ "Other race/ethnicity (vs Non-Hispanic White)",
      TRUE ~ term
    ),
    term_label = fct_reorder(term_label, estimate)
  )

fig1b_obj <- ggplot(plot_hiv, aes(y = term_label, x = estimate, xmin = conf.low, xmax = conf.high)) +
  geom_point(color = "darkred", size = 3) +
  geom_errorbar(width = 0.2, color = "darkred") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  labs(
    title = "B. HIV-specific predictors of HAD (PLWH only)",
    subtitle = "Linear regression; ref: undetectable viral load, male, Non-Hispanic White",
    x = "β (95% CI), years of HAD",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.y = element_text(size = 10, face = "bold")
  )

fig1b_obj

# RETIRED standalone save (kept for reference):
# ggsave(filename = file.path(figures_dir, "Fig2_HIV_Severity_ForestPlot.png"),
#        plot = fig1b_obj, width = 8, height = 6, dpi = 300, bg = "white")

# ---- Combined Figure 1 (Panels A + B stacked vertically via patchwork) ----
# Vertical stacking gives each panel full width — avoids label crowding.
# Tighten title/subtitle spacing and font sizes so they don't overlap.

fig1a_tight <- fig1a_obj +
  theme(
    plot.title    = element_text(face = "bold", size = 12, margin = margin(b = 4)),
    plot.subtitle = element_text(size = 9, margin = margin(b = 8)),
    axis.text.y   = element_text(size = 10)
  )

fig1b_tight <- fig1b_obj +
  theme(
    plot.title    = element_text(face = "bold", size = 12, margin = margin(b = 4)),
    plot.subtitle = element_text(size = 9, margin = margin(b = 8)),
    axis.text.y   = element_text(size = 10, face = "bold")
  )

fig1_combined <- fig1a_tight / fig1b_tight +
  plot_layout(heights = c(1, 1)) +
  plot_annotation(
    title = "Fig. 1. Forest plots of predictors of heart age deviation.",
    caption = paste0(
      "Panel A: predictors of elevated HAD (≥5 years) from multivariable logistic regression ",
      "(odds ratios and 95% CIs; reference categories: HIV-negative, male, Non-Hispanic White, West; ",
      "age per 10-year increment).\n",
      "Panel B: HIV-specific predictors of HAD among people with HIV from multivariable linear regression ",
      "(β coefficients and 95% CIs; reference categories: undetectable viral load, male, ",
      "Non-Hispanic White; CD4 count per 100 cells/μL; age per 10 years)."
    ),
    theme = theme(
      plot.title   = element_text(size = 11, face = "bold", hjust = 0, margin = margin(b = 8)),
      plot.caption = element_text(size = 8, hjust = 0, margin = margin(t = 10))
    )
  )

ggsave(
  filename = file.path(figures_dir, "Fig1_Combined.png"),
  plot = fig1_combined,
  width = 10,
  height = 12,
  dpi = 300,
  bg = "white"
)
message("Combined Fig 1 (Panels A+B, vertical) saved to: ", file.path(figures_dir, "Fig1_Combined.png"))

# ---- Print combined figure inline ----
fig1_combined
```

------------------------------------------------------------------------

## Supplemental Table S4: Mental Health and Social Determinants (was S6)

```{r suppl_s4_mice}
# ==============================================================================
#  MICE Imputation: Mental Health & Social Determinants (Full Sample)
# ==============================================================================

vars_for_mice <- c(
  "heart_age_deviation", "had5",
  "hiv_status", "SEX", "age_decade", "race_eth_4cat", "REGION_factor",
  "CESDCAT", "PTSDCAT", "POTUSE", "COCUSE",
  "NEIGHBSAFE", "LONELY3",
  "viral_suppression", "cd4_100"
)

existing_vars <- vars_for_mice[vars_for_mice %in% names(modeling_data)]
imp_data_raw <- modeling_data %>% select(all_of(existing_vars))

ini <- mice(imp_data_raw, maxit = 0, printFlag = FALSE)
meth <- ini$method
pred <- ini$predictorMatrix

meth["heart_age_deviation"] <- ""
meth["had5"] <- ""

imp_object <- mice(imp_data_raw, method = meth, predictorMatrix = pred,
                   m = 10, printFlag = FALSE, seed = 123)

fit_social_lm <- with(imp_object,
  lm(heart_age_deviation ~ hiv_status + SEX + age_decade + race_eth_4cat +
     CESDCAT + PTSDCAT + NEIGHBSAFE + LONELY3)
)

tbl_social <- tbl_regression(
  fit_social_lm,
  estimate_fun = ~ style_sigfig(.x, digits = 2),
  label = list(
    NEIGHBSAFE ~ "Neighborhood Safety (Higher = Unsafe)",
    LONELY3 ~ "Loneliness Score"
  )
) %>%
  bold_p() %>%
  modify_caption("**Supplemental Table S4. Multiple-imputation model: mental health and social determinants predicting heart age deviation.**")

tbl_social
```

------------------------------------------------------------------------

## Supplemental Table S5 and Figure S1: Interaction Model (was S7)

```{r suppl_s5_and_figs1}
# ==============================================================================
#  Interaction Model: HIV Serostatus × Sex
# ==============================================================================

lm_aim2_int <- lm(
  heart_age_deviation ~ hiv_status * SEX + age_decade + race_eth_4cat + REGION_factor,
  data = modeling_data
)

tbl_aim2_int <- tbl_regression(
  lm_aim2_int,
  label = list(
    hiv_status ~ "HIV Serostatus",
    SEX ~ "Sex",
    `hiv_status:SEX` ~ "Interaction: HIV × Sex"
  )
) %>%
  bold_p() %>%
  modify_caption("**Supplemental Table S5. Interaction model: HIV serostatus × sex predicting heart age deviation.**")

tbl_aim2_int

# --- Supplemental Figure S1: Predicted Marginal Means ---
emm_aim2 <- emmeans(lm_aim2_int, ~ hiv_status | SEX)
emm_aim2_df <- as_tibble(emm_aim2)

ggplot(emm_aim2_df, aes(x = SEX, y = emmean, color = hiv_status, group = hiv_status)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +
  geom_line(position = position_dodge(width = 0.3)) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL),
                position = position_dodge(width = 0.3), width = 0.2) +
  labs(
    title = "Supplemental Fig S1: Predicted heart age deviation by sex and HIV serostatus",
    subtitle = "Estimated marginal means with 95% CIs from interaction model",
    y = "Predicted Heart Age Deviation (Years)",
    x = "Sex",
    color = "HIV Serostatus"
  ) +
  theme_minimal()

ggsave(
  filename = file.path(figures_dir, "FigS1_Emmeans_HAD_Sex_HIV.png"),
  width = 7, height = 5, dpi = 300, bg = "white"
)
message("Suppl Fig S1 saved to: ", file.path(figures_dir, "FigS1_Emmeans_HAD_Sex_HIV.png"))
```

------------------------------------------------------------------------

## Supplemental Figure S2: Heatmap of Prevalence

```{r suppl_figs2_heatmap}
#| fig.width: 10
#| fig.height: 12

# ---- Data Preparation Function ----
prepare_viz_data <- function(data, outcome_var) {

  strat_vars <- c("age_group", "SEX", "race_eth_4cat", "REGION_factor",
                  "bmi_cat", "sbp_cat", "chol_cat", "egfr_cat",
                  "CURSMOKE_BIN", "DIAB_BIN", "HYPERTENSIONMED", "STATINMED")

  var_label_map <- c(
    "age_group" = "Age Group",
    "SEX" = "Sex",
    "race_eth_4cat" = "Race/Ethnicity",
    "REGION_factor" = "Region",
    "bmi_cat" = "BMI Category",
    "sbp_cat" = "SBP Category",
    "chol_cat" = "Cholesterol",
    "egfr_cat" = "eGFR Category",
    "CURSMOKE_BIN" = "Current Smoker",
    "DIAB_BIN" = "Diabetes",
    "HYPERTENSIONMED" = "BP Meds",
    "STATINMED" = "Statin Use"
  )

  plot_data <- purrr::map_dfr(strat_vars, function(v) {
    data %>%
      filter(!is.na(.data[[v]]), !is.na(hiv_status)) %>%
      group_by(hiv_status, Subgroup = .data[[v]]) %>%
      summarise(
        total = n(),
        n_events = sum(.data[[outcome_var]] %in% c("Yes", 1), na.rm = TRUE),
        prev = n_events / total,
        .groups = "drop"
      ) %>%
      mutate(
        Category = var_label_map[v],
        label_text = scales::percent(prev, accuracy = 1)
      )
  })

  plot_data$Category <- factor(plot_data$Category, levels = var_label_map)
  return(plot_data)
}

# ---- Plotting Function ----
create_heatmap_plot <- function(plot_data, title, fill_color = "#08306b") {
  ggplot(plot_data, aes(x = hiv_status, y = Subgroup, fill = prev)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = label_text), color = "black", size = 3) +
    scale_fill_gradient(low = "#f7fbff", high = fill_color,
                        labels = scales::percent, name = "Prevalence") +
    facet_grid(Category ~ ., scales = "free_y", space = "free_y", switch = "y") +
    labs(title = title, x = NULL, y = NULL) +
    theme_minimal(base_size = 12) +
    theme(
      panel.grid = element_blank(),
      strip.text.y.left = element_text(angle = 0, face = "bold", hjust = 1),
      strip.placement = "outside",
      axis.text.x = element_text(face = "bold", size = 10),
      axis.text.y = element_text(size = 9),
      legend.position = "bottom",
      plot.title = element_text(face = "bold", hjust = 0.5),
      strip.background = element_rect(fill = "grey95", color = NA)
    )
}

# Supplemental Fig S2: HAD ≥ 5 heatmap (primary supplemental figure)
data_had5 <- prepare_viz_data(analysis_clean, "had5")
plot_had5 <- create_heatmap_plot(
  data_had5,
  title = "Supplemental Fig S2: Prevalence of Heart Age Deviation ≥5 Years by Subgroup",
  fill_color = "#cb181d"
)
plot_had5

ggsave(filename = file.path(figures_dir, "FigS2_Prevalence_HAD_ge5.png"),
       plot = plot_had5, width = 8.5, height = 11, dpi = 300, bg = "white")

# HAD > 0 heatmap (additional reference, not in main docx)
data_had0 <- prepare_viz_data(analysis_clean, "ha_gt_age")
plot_had0 <- create_heatmap_plot(
  data_had0,
  title = "Prevalence of Heart Age > Chronological Age (HAD > 0)",
  fill_color = "#2171b5"
)
plot_had0

ggsave(filename = file.path(figures_dir, "FigS_Prevalence_HAD_gt_0.png"),
       plot = plot_had0, width = 8.5, height = 11, dpi = 300, bg = "white")

message("Supplemental figures saved to: ", figures_dir)
```

------------------------------------------------------------------------

## Supplemental Figures S3–S5: CD4 Diagnostic Plots

```{r suppl_figs3_5_diagnostics}
# ==============================================================================
#  CD4 Diagnostics — kept as supplemental (per author request)
# ==============================================================================

plwh_diag <- analysis_clean %>%
  filter(hiv_status == "PLWH") %>%
  filter(!is.na(CD4N), !is.na(heart_age_deviation)) %>%
  mutate(
    cd4_cat = case_when(
      CD4N < 200 ~ "<200 cells/mm3",
      CD4N >= 200 & CD4N < 500 ~ "200-499 cells/mm3",
      CD4N >= 500 ~ ">=500 cells/mm3",
      TRUE ~ NA_character_
    ) %>% factor(levels = c("<200 cells/mm3", "200-499 cells/mm3", ">=500 cells/mm3"))
  )

# Supplemental Figure S3: CD4 Count vs. HAD (scatter + linear + LOESS)
p1 <- ggplot(plwh_diag, aes(x = CD4N, y = heart_age_deviation)) +
  geom_point(alpha = 0.5, color = "grey40") +
  geom_smooth(method = "lm", color = "red", fill = "#ffcccc") +
  geom_smooth(method = "loess", color = "blue", se = FALSE, linetype = "dashed") +
  labs(title = "Supplemental Fig S3: CD4 Count vs. Heart Age Deviation",
       subtitle = "Red = Linear Fit, Blue = Loess (Flexible)",
       x = "CD4 Count (cells/mm3)", y = "HAD (Years)") +
  theme_minimal()

# Supplemental Figure S4: HAD Distribution by CD4 Category (Boxplots)
p2 <- ggplot(plwh_diag, aes(x = cd4_cat, y = heart_age_deviation, fill = cd4_cat)) +
  geom_boxplot() +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 3, fill = "white") +
  labs(title = "Supplemental Fig S4: HAD Distribution by CD4 Category",
       x = NULL, y = "Heart Age Deviation") +
  theme_minimal() +
  theme(legend.position = "none", axis.text.x = element_text(angle = 15, hjust = 1))

# Supplemental Figure S5: Age vs. CD4 (Survival bias check)
p3 <- ggplot(plwh_diag, aes(x = AGEATVIS, y = CD4N)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm") +
  labs(title = "Supplemental Fig S5: Age vs. CD4 Count",
       subtitle = "Are older patients having higher CD4s (survival bias)?",
       x = "Chronological Age", y = "CD4 Count") +
  theme_minimal()

(p1 | p2) / p3

ggsave(
  filename = file.path(figures_dir, "FigS3_S5_CD4_Diagnostics.png"),
  plot = (p1 | p2) / p3,
  width = 12, height = 8, dpi = 300, bg = "white"
)
message("Suppl Figs S3–S5 saved to: ", file.path(figures_dir, "FigS3_S5_CD4_Diagnostics.png"))

# Correlation matrix
cor_vars <- plwh_diag %>%
  select(CD4N, heart_age_deviation, heart_age, prevent_risk, AGEATVIS)
print("Correlation Matrix (CD4 and outcomes):")
print(round(cor(cor_vars, use = "pairwise.complete.obs"), 3))

# Sensitivity model excluding extreme CD4 outliers
sensitivity_model <- lm(
  heart_age_deviation ~ viral_suppression + CD4N + AGEATVIS + SEX + race_eth_4cat,
  data = plwh_diag %>% filter(CD4N < 1500)
)
print("Sensitivity Model (Excluding CD4 > 1500):")
print(summary(sensitivity_model)$coefficients["CD4N", ])
```

------------------------------------------------------------------------

# Methods

Analyses were conducted with `r stringr::word(R.Version()$version.string, 1, 3)` with the `tidyverse` (`r packageVersion("tidyverse")`), `rUM` (`r packageVersion("rUM")`), `table1` (`r packageVersion("table1")`) packages used to preprocess and summarize data.[@R-base; @R-tidyverse; @tidyverse2019; @R-rUM; @R-table1]

# Results

# Conclusion

# References {.unnumbered}

```{r}
#| include: false

# automatically create a bib database for loaded R packages & rUM
knitr::write_bib(
  c(
    .packages(),
    "rUM",
    "table1"
  ),
  "packages.bib"
)
```
