---
title: "ECG paper with Claudia and Denise"
author: "Yue Pan"
date: "`r Sys.Date()`"
format:
  html:
    self-contained: true
knitr:
  opts_chunk:      ########## set global options ############
    collapse: true # keep code from blocks together (if shown)
    echo: false    # don't show code
    message: true  # show messages
    warning: true  # show warnings
    error: true    # show error messages
    comment: ""    # don't show ## with printed output
    R.options:    
      digits: 3    # round to three digits
editor: visual
bibliography: [references.bib, packages.bib]
csl: the-new-england-journal-of-medicine.csl
---

```{r}
#| label: tidyverse
#| echo: false

# remove.packages("rlang")
# install.packages("rlang")
library(conflicted)
conflict_prefer("filter", "dplyr", quiet = TRUE)
conflict_prefer("lag", "dplyr", quiet = TRUE)
conflict_prefer("mutate", "dplyr", quiet = TRUE)
conflict_prefer("rename", "dplyr", quiet = TRUE)

# suppressPackageStartupMessages(library(tidyverse))

# suppress "`summarise()` has grouped output by " messages
options(dplyr.summarise.inform=F)


```

# Introduction

## 1. import and check data

```{r}
#| echo: false
#| warning: false
library(tidyverse)
library('redcapAPI')
library('rUM')
library('REDCapR')
library('flextable')
library('dlookr')
library('janitor')
library('dplyr')
library('ggplot2')
if(!require('plyr')) {
    install.packages('plyr')
    library('plyr')
}
library(skimr)
library("stringr") 

# import data
X21076_2_macs <- read_csv("data/X21076_2/X21076_2_macs.csv") %>% 
  arrange(MACSID, VISIT) %>% 
  group_by(MACSID) %>% 
  filter(row_number()==1) %>% 
  ungroup() %>% 
  # select(MC_MI) %>% 
  mutate(ECG_AB = case_when(MC_MI==1 or AFIB==1 ~ "Yes",
                           TRUE ~ "No")) %>% 
  head(ECG_AB)
                           
X21076_2_macs  %>% 
  select(ECG_AB)

  
  
X21076_2_wihs <- read_csv("data/X21076_2/X21076_2_wihs.csv") %>% 
  arrange(WIHSID, VISIT) %>% 
  group_by(WIHSID) %>% 
  filter(row_number()==1) %>% 
  ungroup() %>% 
  skim() %>% flextable


```

## Retrieve data

# Methods

Analyses were conducted with `r stringr::word(R.Version()$version.string, 1, 3)` with the `tidyverse` (`r packageVersion("tidyverse")`), `rUM` (`r packageVersion("rUM")`), `table1` (`r packageVersion("table1")`) packages used to preprocess and summarize data.[@R-base; @R-tidyverse; @tidyverse2019; @R-rUM; @R-table1]

# Results

# Conclusion

# References {.unnumbered}

```{r}
#| include: false

# automatically create a bib database for loaded R packages & rUM
knitr::write_bib(
  c(
    .packages(),
    "rUM",
    "table1"
  ),
  "packages.bib"
)
```
